### 2014-03-09 src/analysis.Rnw
update

# TODO - replace by o.processed.
o.xp <- subset(r.processed, grepl('^r[.].*.m[.]red',ind))
ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)+ myopts
@
\caption{The effect of round(x) reduction, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
\label{fig:xroundsel}
\end{figure*}

\begin{figure*}[t]
<<x.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp <- subset(r.processed, grepl('^rr[.].*.m[.]red',ind))
ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts
@
\caption{The effect of sample(x) reduction(randoop). All are above 0.90 $R^2$.}
\label{fig:xsamplesel}
\end{figure*}
%TODO : See if the following paragraph is needed, or shall we just sink the ceil(x) discussion completely?
Our experiments found that while $round(x)$ and $sample(x)$ produced relatively reasonable reduction of mutants, the $ceil(x)$ criteria failed to produce a reasonable reduction of mutants except for higher power where the reduction was some what close to that produced by $round(x)$ and $sample(x)$ (which was expected). The $R^2$ values of $ceil(x)$ were almost always lower than that produced by $round(x)$ and $sample(x)$ for similar reduction of mutants. For this reason, we do not consider this function again. However, interested parties can refer to our published data.

>>>>

# TODO - replace by o.processed.
o.xp <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)+ myopts
@
\caption{The effect of round(x) reduction, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
\label{fig:xroundsel}
\end{figure*}

\begin{figure*}[t]
<<x.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts
@
\caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
\label{fig:xsamplesel}
\end{figure*}
%TODO : See if the following paragraph is needed, or shall we just sink the ceil(x) discussion completely?
Our experiments found that while $round(x)$ and $sample(x)$ produced relatively reasonable reduction of mutants, the $ceil(x)$ criteria failed to produce a reasonable reduction of mutants except for higher power where the reduction was some what close to that produced by $round(x)$ and $sample(x)$ (which was expected). The $R^2$ values of $ceil(x)$ were almost always lower than that produced by $round(x)$ and $sample(x)$ for similar reduction of mutants. For this reason, we do not consider this function again. However, interested parties can refer to our published data.
